Tutorial: Quantifying Spatially Resolved Hydration Thermodynamics Using Grid Inhomogeneous Solvation Theory [Article v\versionnumber]

### 2024-06-04 manuscript/manuscript.tex
Update manuscript.tex

Due to the varying sizes of the boxes, the reference energies used in this context may not align with those specified in the Amber manual. Generally, it is recommended that the size of the reference water box closely matches that of the production system. Therefore, it is advisable to conduct your own reference calculations, especially for systems that are either very large or very small. While the impact on density is not as pronounced, deviations from the specified settings can lead to differences of up to 0.005 kcal/mol in the $E_{ww, norm}$ value for water boxes. These discrepancies, when summing over large grid regions, have the potential to introduce significant errors due to incorrect referencing.

>>>>

Due to the varying sizes of the boxes, the reference energies used in this context may not align with those specified in the Amber manual. Generally, it is recommended that the size of the reference water box closely matches that of the production system. Therefore, it is advisable to conduct your own reference calculations, especially for systems that are either very large or very small. While the impact on density is not as pronounced, deviations from the specified settings can lead to differences of up to 0.005 kcal/mol in the energy per water molecule ($E_{ww, norm}$) for water boxes. These discrepancies, when summing over large grid regions, have the potential to introduce significant errors due to incorrect referencing.
